---
title: "KEA Monitoring Protocol Development"
author: "Adrienne St. Clair"
date: "`r format(Sys.time(), 'd B, Y')`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide") 

library(here)
library(tidyverse)
library(ggplot2)
library(xlsx)
library(mosaic)
library(purrr)
library(kableExtra)
library(plotrix)
```

```{r directories}
code_dir    <- "01_code"
raw_data    <- "02_raw-data"
data_dir    <- "03_clean-data"
results_dir <- "04_results"
```

# Going from Percent Cover to 95 confidence intervals

If we have a sample of percent covers--1 per transect. How do we find the margin of error and the 95 confidence intervals?

I'll use some example data from the Turnstone monitoring done at Smith Bybee. I pulled the percent cover from their forested wetland habitat

```{r}
data <- as.numeric(c(".61", ".36", ".49", ".05", ".58", ".45", ".60", ".68", ".60", ".20", ".32"))

hist(data)

```

following [this tutorial](https://www.youtube.com/watch?v=ZkCDYAC2iFg), we will resample the data with replacement at the original 11 observations per replicate and replicate it 100,000 times. This should give us a normally distributed sample of means.

```{r}
# find the mean of the data
xbar <- mean(data)

# test out this code
do(5) * mean(sample(data, 11, replace = TRUE))

tri11 <- do(100000) * mean(sample(data, 11, replace = TRUE))


tri11 %>% 
  ggplot(aes(mean)) +
  geom_histogram()

```

From these data we can pull the standard deviation and the 95% confidence intervals.

```{r}



se_tutorial <- sd( ~ mean, data = tri11)

se_math <- (sd(data))/sqrt(length(data)) 

se_plotrix <- std.error(data)

1.96 * se_plotrix

(xbar - 1.96 * se)
(xbar + 1.96 * se)
```

But, we don't really need to be 95% certain of the mean, we're good with being 80% certain. The function `confint()` allows me to set the level of certainty.

```{r}
confint(tri11, level = 0.80, method = "percentile")
```

So, we can be 80% sure that our estimate of 44% cover that the mean is somewhere between 37 and 52%.

## Sample Size

```{r}

var(data)


```

from: Elbers 2995

Two calculations need to be made.

First, the sample size of transects within a cluster is calculated ($n_{2}$). Then the number of clusters to be sampled is calculated ($n_{1}$).

$n_{2} = \sqrt{\frac{c_{1}(1-p)}{c_{2}p}}$
